Dynastic Extinctions and Urban Economic Development: \\Evidence from the Holy Roman Empire\footnote{I thank Davide Cantoni, Matthias Weigand, and my RA colleagues at the Chair of Economic History for helpful comments and feedback.}

### 2023-06-18 paper/paper.tex
#25 first half of empirics section

\begin{equation}
    construction_{it} = \alpha_i + \delta_t + \mathbf{1}(S_{it} > 0) + 
    \sum_{\tau = -100}^{200} \mathbf{1}(t = e^{NewState}_i + \tau)\pi_t + \varepsilon_{it},
\end{equation}

where the outcome $construction_{it}$ is an indicator that equals 1 if any construction activity was recorded in city $i$ and period $t$,  the variable $S_{it}$ is the number of times a city switched states in period $t$, the variable $e^{NewState}_i$ denotes the first period in which city $i$ belongs to a different state than the previous, and $\alpha_i$ and $\delta_t$ denote city and period fixed effects.

Some comments on this. First, it may seem like a good idea to include state fixed effects. But I cannot because the hypothesised selection effect works through an improvement in state quality. State fixed effects would absorb the variation in time-invariant state quality.

@@

Next I tried to find the effect of state power - the effect of the difference in selection for state power between conquests and successions:

I use a triple interaction. I extend the previous regression

\begin{multline}
    construction_{it} = \alpha_i + \delta_t + \mathbf{1}(S_{it} > 0) +
    \mathbf{1}(t \ge e^{NewState}_i)\beta +
    \mathbf{1}(t \ge e^{NewState}_i) \times C_i \times \theta + \varepsilon_{it}
\end{multline}

Blah blah.

@@

>>>>

\begin{equation}
\label{eq:sw22}
    construction_{it} = \alpha_i + \delta_t + \mathbf{1}(S_{it} > 0)\beta + 
    \sum_{\tau = -100}^{200} \mathbf{1}(t = e^{NewState}_i + \tau)\pi_\tau + \varepsilon_{it},
\end{equation}

where the outcome $construction_{it}$ is an indicator that equals 1 if any construction activity was recorded in city $i$ and period $t$, the variable $S_{it}$ is the number of times a city switched states in period $t$, the variable $e^{NewState}_i$ denotes the first period in which city $i$ belongs to a different state than the previous, and $\alpha_i$ and $\delta_t$ denote city and period fixed effects. The coefficients of interest are the dynamic effects $\pi_\tau$ of switching to a new state permanently.

Since the outcome is binary, equation \ref{eq:sw22} represents a linear probability model: we model $construction_{it}$ as a random variable that follows a Bernoulli distribution with a probability parameter $p$ that is conditional on the right-hand side variables. This way we can interpret the values of coefficients as differences in the probability of recorded construction activity in a given period.

The coefficient $\pi_\tau$ for given $\tau$ is the difference in the probability of construction between two cities $i$ and $j$ with identical time-invariant characteristics, in the same period, who undergo the same amount of switching turmoil in this period. The only difference is that one city underwent a lasting switch to another state $\tau$ periods ago, while the other did not.

% Since comparisons between cities at different \tau are problematic, we also use the Sun and Abraham estimator (as do SW22).

Remember, we expect this difference to stem from the fact that switching states generally means switching to a higher-quality state (due to selection). As such, even though it would be possible in principle to include state fixed effects, it is not a good idea here: state fixed effects would absorb the variation in state quality whose effects we want to capture in $\pi_\tau$.

@@

Next I tried to find the effect of state power - the effect of the difference in selection for state power between conquests and successions.

I switch to a simple difference-in-differences specification for clarity. I extend the previous regression by interacting with the type of the ownership change:

\begin{equation}
\label{eq:baseline}
    construction_{it} = \alpha_i + \delta_t + \mathbf{1}(S_{it} > 0)\beta +
    \mathbf{1}(t \ge e^{NewState}_i)\pi +
    \mathbf{1}(t \ge e^{NewState}_i) T_i \theta + \varepsilon_{it}
\end{equation}

a second-order interaction necessitates that the first-order interaction pattern and associated coefficient (whether zero or non-zero) is itself different depending on the level of a third predictor. (from stackexchange)

Blah blah. Equation \ref{eq:baseline}

@@

\section{Discussion}

\section{Conclusion}
